Synthesising Complex Termination Arguments

### 2014-06-23 papers/termination/paper.tex
Remove a bunch of LKC vs. linearity stuff
revised motivation

\section{Motivational Examples} \label{sec:motivation}
We next discus some intricate examples that prove challenging for existent termination analysis.
%a few examples that illustrate the difficulties in termination checking for low-level code. In particular, they denote situations that arise 
%frequently in practise and are not properly handled by existing techniques.

@@

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
  while (x != 0) {
    if (x > 0)
      x--;
    else
      x++;
  }
\end{lstlisting}
\caption{}
 \label{fig:motivation.c}
\end{subfigure}%

\end{tabular}
\end{figure*}

>>>>

\section{Motivational Examples} \label{sec:motivation}
In the previous sections, we have discussed some of the assumptions made by existent termination analyses (see Figure~\ref{fig:handletable}). 
Now, we provide some simple examples that broke those assumptions and

We next discus some intricate examples that prove challenging for existent termination analysis.
%a few examples that illustrate the difficulties in termination checking for low-level code. In particular, they denote situations that arise 
%frequently in practise and are not properly handled by existing techniques.

@@

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}[language=C]
 while(x > 0) x++;
 \end{lstlisting}
\caption{}
 \label{fig:motivation.c}
\end{subfigure} \\

\hline

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
  while ( q >= 0 ) {
    q = q - y;
    y = y + 1;
  }
\end{lstlisting}
\caption{}
 \label{fig:motivation.d}
\end{subfigure}

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
while (x > 0.0) x -= 1.0;
\end{lstlisting}
\caption{}
 \label{fig:motivation.f}
\end{subfigure}

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
while (x > 0.0) x *= 0.5;
\end{lstlisting}
\caption{}
 \label{fig:motivation.g}
\end{subfigure} \\
\hline

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
  while (x != 0) {
    if (x > 0)
      x--;
    else
      x++;
  }
\end{lstlisting}
\caption{}
 \label{fig:motivation.h}
\end{subfigure}

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
while (x > 0 && y > 0 && z > 0) {
    if (y > x) {
      y = z;
      x = nondet();
      z = x - 1;
    } else {
      z = z - 1;
      x = nondet();
      y = x - 1;
    }
}
\end{lstlisting}
\caption{}
 \label{fig:motivation.h}
\end{subfigure}

\end{tabular}
\caption{Sample programs}\label{fig:motivation}
\end{figure*}
